Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Add test-shouldbe to contributions

The contributions of this paper are:

\begin{itemize}
\item Introduced \doctest{} from Python community to Haskell community
and integrated it with QuickCheck
(Section \ref{sec:for-users} and Section \ref{sec:doctest})
%% \item Introduced {\tt Hspec} from Ruby community to Haskell community and
%% integrated it with QuickCheck
%% (Section \ref{sec:for-developers} and Section \ref{sec:hspec})
\item Show best current practice of BDD in Haskell using \doctest{} and \hspec{} (Section \ref{ref:Best-current-practice})
\end{itemize}

>>>>

Our contributions are:

\begin{itemize}
\item
    Add support for QuickCheck properties to \doctest{}
    (Section \ref{sec:for-users} and Section \ref{sec:doctest})

\item
    Introduce a set of combinators to set of expectations about \emph{code
    examples} for use with \hspec{}.
%% \item Introduced {\tt Hspec} from Ruby community to Haskell community and
%% integrated it with QuickCheck
%% (Section \ref{sec:for-developers} and Section \ref{sec:hspec})
\item Show best current practice of BDD in Haskell using \doctest{} and
    \hspec{} (Section \ref{ref:Best-current-practice})
\end{itemize}
